Evolutionary algorithms in a volunteer computing system: performance assessment

### 2016-03-11 PPSN2016/paper.Rnw
Including aggregate count

experiment.aggregates <- data.frame(Experiment=character(),
                                     milliseconds=character(),
                                     IPs=character(),
                                     actualIPs = character(),
                                     PUTss = character(),
                                     actualPUTs = character());

experiment.aggregates.filtered <- data.frame(Experiment=character(),
                                             milliseconds=character(),
                                             IPs=character(),
                                             actualIPs = character(),
                                             PUTss = character(),
                                             actualPUTs = character());

@@

    experiment.aggregates <- rbind( experiment.aggregates,
                                   data.frame( Experiment=i,                   
                                              milliseconds=median(as.integer(this.data$milliseconds)),
                                              IPs=median(as.integer(this.data$IPs)),
                                              actualIPs=median(as.integer(this.data$actualIPs)),
                                              PUTs=median(as.integer(this.data$PUTs)),
                                              actualPUTs=median(as.integer(this.data$actualPUTs)))
                                   )

@@

    this.data <- this.data[this.data$actualPUTs>=10,]
    experiment.aggregates.filtered <- rbind( experiment.aggregates.filtered,
                                            data.frame( Experiment=i,                   
                                                       milliseconds=median(as.integer(this.data$milliseconds)),
                                                       IPs=median(as.integer(this.data$IPs)),
                                                       actualIPs=median(as.integer(this.data$actualIPs)),
                                                       PUTs=median(as.integer(this.data$PUTs)),
                                                       actualPUTs=median(as.integer(this.data$actualPUTs))))

>>>>

experiment.aggregates <- data.frame(Experiment=character(),
                                    milliseconds=character(),
                                    IPs=character(),
                                    actualIPs = character(),
                                    PUTss = character(),
                                    actualPUTs = character(),
                                    count = character())

experiment.aggregates.filtered = experiment.aggregates

@@

    experiment.aggregates <- rbind( experiment.aggregates,
                                   data.frame( Experiment=i,                   
                                              milliseconds=median(as.integer(this.data$milliseconds)),
                                              IPs=median(as.integer(this.data$IPs)),
                                              actualIPs=median(as.integer(this.data$actualIPs)),
                                              PUTs=median(as.integer(this.data$PUTs)),
                                              actualPUTs=median(as.integer(this.data$actualPUTs)),
                                              count= length(this.data$IPs))
                                   )

@@

    this.data <- this.data[this.data$actualPUTs>=10,]
    experiment.aggregates.filtered <- rbind( experiment.aggregates.filtered,
                                            data.frame( Experiment=i,                   
                                                       milliseconds=median(as.integer(this.data$milliseconds)),
                                                       IPs=median(as.integer(this.data$IPs)),
                                                       actualIPs=median(as.integer(this.data$actualIPs)),
                                                       PUTs=median(as.integer(this.data$PUTs)),
                                                       actualPUTs=median(as.integer(this.data$actualPUTs)),
                                                       count= length(this.data$IPs)))
